Illusion Game Validation (Study 2)

### 2022-09-06 study2/study2.Rmd
figs

```{r message=FALSE, warning=FALSE, cache=cache}
plot_ppcheck(model_delboeuf_rt, gam_delboeuf_rt)

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
plot_ppcheck(model_ebbinghaus_rt, gam_ebbinghaus_rt)

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
plot_ppcheck(model_rodframe_rt, gam_rodframe_rt)

@@

plot_ppcheck(model_verticalhorizontal_rt, gam_verticalhorizontal_rt)
# performance::check_model(model_verticalhorizontal_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_zollner_rt, gam_zollner_rt)
# performance::check_model(model_zollner_rt)
# parameters::parameters(model)

@@

plot_ppcheck(model_white_rt, gam_white_rt)
# performance::check_model(model_white_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_mullerlyer_rt, gam_mullerlyer_rt)
# performance::check_model(model_mullerlyer_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_ponzo_rt, gam_ponzo_rt)
# performance::check_model(model_ponzo_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_poggendorff_rt, gam_poggendorff_rt)
# performance::check_model(model_poggendorff_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_contrast_rt, gam_contrast_rt)
# performance::check_model(model_contrast_rt)
# parameters::parameters(model)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
data <- rbind(
  extract_random(model_delboeuf_err, "Delboeuf"),
  # extract_random(model_delboeuf_rt, "Delboeuf"),
  extract_random(model_ebbinghaus_err, "Ebbinghaus"),
  # extract_random(model_ebbinghaus_rt, "Ebbinghaus"),
  extract_random(model_rodframe_err, "Rod-Frame"),
  # extract_random(model_rodframe_rt, "Rod-Frame"),
  extract_random(model_verticalhorizontal_err, "Vertical-Horizontal"),
  # extract_random(model_verticalhorizontal_rt, "Vertical-Horizontal"),
  extract_random(model_zollner_err, "Zöllner"),
  # extract_random(model_zollner_rt, "Zöllner"),
  extract_random(model_white_err, "White"),
  # extract_random(model_white_rt, "White"),
  extract_random(model_mullerlyer_err, "Müller-Lyer"),
  # extract_random(model_mullerlyer_rt, "Müller-Lyer"),
  extract_random(model_ponzo_err, "Ponzo"),
  # extract_random(model_ponzo_rt, "Ponzo"),
  extract_random(model_poggendorff_err, "Poggendorff"),
  # extract_random(model_poggendorff_rt, "Poggendorff"),
  extract_random(model_contrast_err, "Contrast")
  # extract_random(model_contrast_rt, "Contrast")
) |> 
  filter(
    !str_detect(Parameter, "Intercept_"),
    !str_detect(Parameter, "Cong"),
    !str_detect(Parameter, "Cong_Prob"),
    !str_detect(Parameter, "Null_"),
    !str_detect(Parameter, "Diff_"))  |> 
  mutate(Parameter = str_remove(Parameter, "_Prob"))

@@

p_ill <- 
  (p_delboeuf + p_ebbinghaus + 
     p_rodframe + p_verticalhorizontal +
     p_zollner + p_white +
     p_mullerlyer + p_ponzo +
     p_poggendorff + p_contrast) + 
    patchwork::plot_layout(ncol= 5, nrow=2)

>>>>

```{r message=FALSE, warning=FALSE, cache=cache}
# plot_ppcheck(model_delboeuf_rt, gam_delboeuf_rt)

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
# # plot_ppcheck(model_ebbinghaus_rt, gam_ebbinghaus_rt)

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
# plot_ppcheck(model_rodframe_rt, gam_rodframe_rt)

@@

# plot_ppcheck(model_verticalhorizontal_rt, gam_verticalhorizontal_rt)
# performance::check_model(model_verticalhorizontal_rt)
# parameters::parameters(model)
```

@@

# plot_ppcheck(model_zollner_rt, gam_zollner_rt)
# performance::check_model(model_zollner_rt)
# parameters::parameters(model)

@@

# plot_ppcheck(model_white_rt, gam_white_rt)
# performance::check_model(model_white_rt)
# parameters::parameters(model)
```

@@

# plot_ppcheck(model_mullerlyer_rt, gam_mullerlyer_rt)
# performance::check_model(model_mullerlyer_rt)
# parameters::parameters(model)
```

@@

# plot_ppcheck(model_ponzo_rt, gam_ponzo_rt)
# performance::check_model(model_ponzo_rt)
# parameters::parameters(model)
```

@@

# plot_ppcheck(model_poggendorff_rt, gam_poggendorff_rt)
# performance::check_model(model_poggendorff_rt)
# parameters::parameters(model)
```

@@

# plot_ppcheck(model_contrast_rt, gam_contrast_rt)
# performance::check_model(model_contrast_rt)
# parameters::parameters(model)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
data <- rbind(
  extract_random(model_delboeuf_err, "Delboeuf"),
  # extract_random(model_delboeuf_rt, "Delboeuf"),
  extract_random(model_ebbinghaus_err, "Ebbinghaus"),
  # extract_random(model_ebbinghaus_rt, "Ebbinghaus"),
  extract_random(model_rodframe_err, "Rod-Frame"),
  # extract_random(model_rodframe_rt, "Rod-Frame"),
  extract_random(model_verticalhorizontal_err, "Vertical-Horizontal"),
  # extract_random(model_verticalhorizontal_rt, "Vertical-Horizontal"),
  extract_random(model_zollner_err, "Zöllner"),
  # extract_random(model_zollner_rt, "Zöllner"),
  extract_random(model_white_err, "White"),
  # extract_random(model_white_rt, "White"),
  extract_random(model_mullerlyer_err, "Müller-Lyer"),
  # extract_random(model_mullerlyer_rt, "Müller-Lyer"),
  extract_random(model_ponzo_err, "Ponzo"),
  # extract_random(model_ponzo_rt, "Ponzo"),
  extract_random(model_poggendorff_err, "Poggendorff"),
  # extract_random(model_poggendorff_rt, "Poggendorff"),
  extract_random(model_contrast_err, "Contrast")
  # extract_random(model_contrast_rt, "Contrast")
) |> 
  filter(
    !str_detect(Parameter, "Intercept_"),
    !str_detect(Parameter, "Cong"),
    !str_detect(Parameter, "Cong_Prob"),
    !str_detect(Parameter, "Null_"),
    !str_detect(Parameter, "Diff_"))  |> 
  mutate(Parameter = str_remove(Parameter, "_Prob"))

@@

# Vertical
p_ill <- 
  (p_delboeuf + p_ebbinghaus + 
     p_rodframe + p_verticalhorizontal +
     p_zollner + p_white +
     p_mullerlyer + p_ponzo +
     p_poggendorff + p_contrast) + 
    patchwork::plot_layout(ncol= 2, nrow=5)

ggsave("figures/figure_ill2.png", p_ill, height = 30, width = 20, dpi=300)

# Horizontal
p_ill <- 
  (p_delboeuf + p_ebbinghaus + 
     p_rodframe + p_verticalhorizontal +
     p_zollner + p_white +
     p_mullerlyer + p_ponzo +
     p_poggendorff + p_contrast) + 
    patchwork::plot_layout(ncol= 5, nrow=2)
